---
title: "RMarkdown for Initial Mysis GAM"
author: "Sarah Lawhun"
date: "2023-01-31"
output: github_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(rmarkdown)
library(mgcv)

```
**1. Load mgcv package `library(mgcv)`** <br>
**2. Read GLNPO csv (for this test, I have already filtered to just Lake Michigan Data).Take a look at the column names.**
```{r}
GLNPO <- read.csv("C:\\Users\\sarah\\Documents\\Cornell\\Mysid Data\\GAM\\Step5_OutputByStation.csv")

colnames(GLNPO)
```
**3. Identify variables of interest for GAM:**
```{R}
Yr <- GLNPO$Year_
Dens <- GLNPO$AvgDens
Bmss <- GLNPO$AvgBmss_mg
```
**4. Run your GAM with x(Yr) and y(Dens) and view the summary information for the plot:**
```{r}
DensGAM <- gam(Dens ~ s(Yr))
summary(DensGAM)
```
**5. Plot a basic version of your GAM: `plot(DensGAM)`**
<br>

```{r, echo=FALSE}
plot(DensGAM)
```
<br>
<br>

Kind of plain, womp womp

<br>
<br>

**6. Spice the plot up**

<br>

```{r, echo=FALSE}
plot(DensGAM, bg="red", col="#336666", xlab = "Year", ylab = "Average Density", main = "Mysis Density in Lake Michigan 2006-2021 Using GLNPO Data")
```

<br>
<br>

I added x and y labels, a title, and a color. I want to add more soon

**7. Run your GAM with x(Yr) and y(Bmss) and view the summary information for the plot:**
```{r}
BmssGAM <- gam(Bmss ~ s(Yr))
summary(BmssGAM)
```
<br>
**8. Plot biomass GAM `plot(BmssGAM)`:**
```{r, echo=FALSE}
plot(BmssGAM)
```


